---
title: "[Project]"
author: "[Samuel Navias]"
subtitle: MGSC 310 Project Summary Statistics
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}
# Please leave this code chunk as is. It makes some slight formatting changes to alter the output to be more aesthetically pleasing. 

library(knitr)

# Change the number in set seed to your own favorite number
set.seed(1818)
options(width=70)
options(scipen=99)


# this sets text outputted in code chunks to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = FALSE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               # change fig.width and fig.height to change the code height and width by default
               fig.width = 5.5,  
               fig.height = 4.5,
               fig.align='center')


```

```{r setup-2}
# Always print this out before your assignment
sessionInfo()
getwd()

```


<!-- ### start answering your problem set here -->
<!-- You may export your homework in either html or pdf, with the former usually being easier. 
     To export or compile your Rmd file: click above on 'Knit' then 'Knit to HTML' -->
<!-- Be sure to submit both your .Rmd file and the compiled .html or .pdf file for full credit -->


```{r setup-3}
# load all your libraries in this chunk 
library('tidyverse')
library('ggplot2')
library('forcats')
library('dplyr')
library('readr')
library('ggrepel')
library('plotROC')
library('rsample')
# note, do not run install.packages() inside a code chunk. install them in the console outside of a code chunk. 

```



## Loading in Data 

1.1) 

```{r}
#Loading in the data and glimpse 
DF <- read_csv("datasets/supermarket_sales.csv")
glimpse(DF)

#Removing the unnecessary columns:Invoice ID, Date, and Time
#The cleaner data is now saved as DFtwo
#DFtwo is not the final cleaned version only an improvement 

DFtwo <- select(DF, -`Invoice ID`, -Date, -Time)
glimpse(DFtwo)

```


1.2) Making vectors to convert into a tibble to present some summary statistics of the Raw data (minus the columns that were removed above). SD of gross margin percentage is 0 so the variable is useless.

```{r}
#Vector for the variable names
vector0 <- c(
"Unit price",
"Quantity",
"Tax 5%",
"Total",
"cogs",
"gross margin percentage",
"gross income",
"Rating"
)

#Vector for the variable averages
vector1 <- c(
mean(DFtwo$`Unit price`),
mean(DFtwo$Quantity),
mean(DFtwo$`Tax 5%`),
mean(DFtwo$Total),
mean(DFtwo$cogs),
mean(DFtwo$`gross margin percentage`),
mean(DFtwo$`gross income`),
mean(DFtwo$Rating)
)

#Vector for the variable standard deviations 
vector2 <- c(
sd(DFtwo$`Unit price`),
sd(DFtwo$Quantity),
sd(DFtwo$`Tax 5%`),
sd(DFtwo$Total),
sd(DFtwo$cogs),
sd(DFtwo$`gross margin percentage`),
sd(DFtwo$`gross income`),
sd(DFtwo$Rating)
)

#Vector for the variable max's
vector3 <- c(
max(DFtwo$`Unit price`),
max(DFtwo$Quantity),
max(DFtwo$`Tax 5%`),
max(DFtwo$Total),
max(DFtwo$cogs),
max(DFtwo$`gross margin percentage`),
max(DFtwo$`gross income`),
max(DFtwo$Rating)
)

#Vector for the variable min's
vector4 <- c(
min(DFtwo$`Unit price`),
min(DFtwo$Quantity),
min(DFtwo$`Tax 5%`),
min(DFtwo$Total),
min(DFtwo$cogs),
min(DFtwo$`gross margin percentage`),
min(DFtwo$`gross income`),
min(DFtwo$Rating)
)

#Creating the tibble
tibble(`Variables` = vector0,
       `Mean` = vector1,
       `Standard Deviation` = vector2,
       `Max` = vector3,
       `Min` = vector4)


```


## Cleaning The Data | Making some plots

2.1) Gross margin percentage removed. Payment, Gender, Branch, City, Product line, Customer type transformed into factor variables. Also made a binary variable to see if a store is considered good or not based on if it got a rating of 8 or higher.


```{r}
DFthree <-  select(DFtwo, -`gross margin percentage`)

DFthree <- DFthree %>% 
  mutate(Payment = as_factor(Payment)) %>% 
  mutate(Gender = as_factor(Gender)) %>% 
  mutate(Branch = as_factor(Branch)) %>% 
  mutate(City = as_factor(City)) %>% 
  mutate(`Product line` = as_factor(`Product line`)) %>% 
  mutate(`Customer type` = as_factor(`Customer type`))

DFthree <- DFthree %>% 
  mutate(goodStore = ifelse(Rating > 8,1,0))

drop_na(DFthree)

```


```{r}
summary(DFthree)
```


```{r}

DFfour <- DFthree %>% 
  mutate(`Unit price` = log(`Unit price`)) %>% 
  mutate(`Quantity` = log(`Quantity`)) %>% 
  mutate(`Tax 5%` = log(`Tax 5%`)) %>% 
  mutate(`Total` = log(`Total`)) %>% 
  mutate(`cogs` = log(`cogs`)) %>% 
  mutate(`gross income` = log(`gross income`)) %>% 
  mutate(`Rating` = log(`Rating`))

DFfive <- DFthree %>% 
  mutate(`Unit price` = log(`Unit price`)) %>% 
  mutate(`Quantity` = as_factor(`Quantity`)) %>% 
  mutate(`Tax 5%` = log(`Tax 5%`)) %>% 
  mutate(`Total` = log(`Total`)) %>% 
  mutate(`cogs` = log(`cogs`)) %>% 
  mutate(`gross income` = log(`gross income`)) %>% 
  mutate(`Rating` = log(`Rating`))

DFfive
```



2.2) Making some plots



This plot is interesting because it shows that the average rating for grocery stores in Mandalay is slightly worse than the the average rating in Naypyitaw and Yangon
```{r}
ggplot(DFthree, aes(x=Branch, y=Rating)) + 
  geom_boxplot()

```

This plot is interesting because it shows that the cogs really has no affect on the rating. Personally  I thought that people who would spend more would tend to have given a higher rating. Because I feel that when I go to the store and spend less money I am usually going to pick up an item that I forgot and I would be upset because I had to go back to the store and I would give a worse rating.  
```{r}
ggplot(data = DFthree, aes(x = `cogs`, y = `Rating`)) + 
  geom_point() + 
  geom_point(aes(colour = factor(`Product line`))) 



```



```{r}
ggplot(data = DFthree, aes(x = `cogs`, y = `Rating`)) + 
  facet_wrap(~`Product line`) + 
  geom_point(alpha = 4/7, aes(colour = factor(`Product line`))) 

```



#Making the first logistic regression model:

Splitting the various transformed data sets:
```{r}
set.seed(1223)

DFthree_split <- initial_split(DFthree, prop = 0.80) 

DFthree_train <- training(DFthree_split)
DFthree_test <- testing(DFthree_split)

```


Building the model. Summary command run and coefficients exponentiated 
```{r}
logit1 <- glm(goodStore ~ Branch + `Customer type` + Gender + cogs + Payment + Quantity,
              data = DFthree_train,
              family = "binomial")

summary(logit1)

exp(logit1$coefficients)
```



```{r}
scoresTrain <- predict(logit1, newdata = DFthree_train,
            type ="response")

scoresTest <- predict(logit1, newdata = DFthree_test,
            type ="response")

results_train <- tibble(
  `true_class` = as.numeric(DFthree_train$goodStore),
  `prob_event` =  scoresTrain
)

results_test <- tibble(
  `true_class` = as.numeric(DFthree_test$goodStore),
  `prob_event` =  scoresTest
)

```


```{r}
ROCTrain <- ggplot(results_train, 
            aes(m = prob_event, d = true_class)) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.9,0.8,0.7,0.5,0.3,0.2,0.1)) +
  theme_minimal(base_size = 16) + 
  xlab("Train: False Positive Rate") + 
  ylab("Train: True Positive Rate")

ROCTest <- ggplot(results_test, 
            aes(m = prob_event, d = true_class)) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.9,0.8,0.7,0.5,0.3,0.2,0.1)) +
  theme_minimal(base_size = 16) + 
  xlab("Test: False Positive Rate") + 
  ylab("Test: True Positive Rate")


ROCTrain
ROCTest
```

```{r}
calc_auc(ROCTrain)
calc_auc(ROCTest)
```


#Building a the same model but with log transformed vars
```{r}
DFfive_split <- initial_split(DFfive, prop = 0.80) 

DFfive_train <- training(DFfive_split)
DFfive_test <- testing(DFfive_split)

```


```{r}
logit2 <- glm(goodStore ~ Branch + `Customer type` + Gender + `Unit price` + Payment + Quantity,
              data = DFfive_train,
              family = "binomial")

summary(logit2)

exp(logit1$coefficients)

```


```{r}
scoresTrain2 <- predict(logit2, newdata = DFfive_train,
            type ="response")

scoresTest2 <- predict(logit2, newdata = DFfive_test,
            type ="response")

results_train2 <- tibble(
  `true_class` = as.numeric(DFfive_train$goodStore),
  `prob_event` =  scoresTrain
)

results_test2 <- tibble(
  `true_class` = as.numeric(DFfive_test$goodStore),
  `prob_event` =  scoresTest
)
```



```{r}
ROCTrain <- ggplot(results_train2, 
            aes(m = prob_event, d = true_class)) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.9,0.8,0.7,0.5,0.3,0.2,0.1)) +
  theme_minimal(base_size = 16) + 
  xlab("Train: False Positive Rate") + 
  ylab("Train: True Positive Rate")

ROCTest <- ggplot(results_test2, 
            aes(m = prob_event, d = true_class)) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.9,0.8,0.7,0.5,0.3,0.2,0.1)) +
  theme_minimal(base_size = 16) + 
  xlab("Test: False Positive Rate") + 
  ylab("Test: True Positive Rate")


ROCTrain
ROCTest
```

